% ------------------------------------------------------------------- %
% Licensed under the Creative Commons Attribution 3.0 Unported
%   Created by Alessandro
%   Modified by Drew Cross <mstngdrew212@gmail.com>
% ------------------------------------------------------------------- %

\documentclass[10pt]{article}

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry}
\usepackage{bbding}
\usepackage{amssymb}
\usepackage{eurosym}
\usepackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}

% Email color
\definecolor{linkcolour}{HTML}{0000FF}
% Light Blue
\definecolor{shade}{HTML}{D4D7FE}
% Nearly black
\definecolor{text1}{HTML}{2b2b2b}
% Maroon
\definecolor{headings}{HTML}{701112}

\hypersetup{colorlinks,breaklinks,
            urlcolor=linkcolour,
            linkcolor=linkcolour}

\usepackage{fancyhdr}               %custom footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\usepackage{titlesec}               %custom \section

\titleformat{\section}
    {\color{headings}
        \scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]

\titlespacing{\section}{0pt}{0pt}{5pt}



%fonts

\begin{document}

\color{text1}

%   <<<< TITLE >>>>
    \par{\centering
        {\sffamily\Huge Drew Cross
    }\\[10pt]
    \par{\centering
    \hrule
    \\[35pt]


%START of left-hand side minipage
\begin{minipage}[t]{0.5\textwidth} 
    \vspace{0pt}



\section{Education}

\begin{tabular}{rl}

    % EDUCATION -1-
    \textsc{May} 2013 & \textbf{University of Illinois}, Champaign \\
     & Bachelor of Science - Computer Science \\
& (Expected) \\[5pt]

    % EDUCATION -2-
     \textsc{May} 2010 & \textbf{Black Hawk College}, Moline\\
     & Associate of Science - Engineering Transfer\\


\end{tabular}\\[10pt]


% <<<< NEW SECTION >>>>
\section{Coursework In Computer Science}
    \raggedright
    \textsc{\textbf{Completed Courses:}}\\[1pt]
    CS 125: Introduction to Computer Science\\
    CS 173: Discreet Structures\\
    CS 231: Computer Architecture \\
    CS 225: Data Structures \\[10pt]
    \textsc{\textbf{Currently Enrolled Courses:}}\\[1pt]
    CS 241: Systems Programming\\
    CS 232: Computer Architecture II \\
    CS 411: Database Systems \\[15pt]


% <<<< NEW SECTION >>>>
\section{Work Experience}

    \raggedleft
    \textsc{\normalsize Summer 2012}\par
    \raggedright\large \textsc{Intern - Software Development Engineer in Test} \\
    \emph{Microsoft Corporation} - Seattle, WA \\[5pt]

    \normalsize{ Worked on Windows Server testing the Hypervisor subsystem. \\[10pt]
    }

    % WORK EXPERIENCE -1-
    \raggedleft
    \textsc{\normalsize January 2011 - Present}\par
    \raggedright\large \textsc{Intern - IT/Systems} \\
    \emph{State Farm Insurance} - Champaign, IL \\[5pt]

    \normalsize{
    Researched and developed new and innovative ways to improve the insurance industry
    through technology and software. Extensive focus on computer vision and augmented reality.
    Frequently worked with OpenCV and Point Cloud Library. \\[10pt]
    }

    % WORK EXPERIENCE -3-
    \raggedleft
    \textsc{\normalsize July 2004 - August 2010}\par
    \raggedright\large \textsc{Shift Manager} \\
    \emph{McDonald's Corporation} - Geneseo, IL \\[5pt]

    \normalsize{
    Responsibilities included: Systems efficiency, financial logistics,
    supply logistics, and personnel logistics.\\[10pt]
    }


%END of left-hand side minipage
\end{minipage}
\hfill
%START of right-hand side minipage
\begin{minipage}[t]{0.44\textwidth}
    \vspace{0pt}

\colorbox{shade}{\textcolor{text1}{
    \begin{tabular}{c|p{7cm}}
        \raisebox{-3pt}{\Phone}         &(Removed) \\
        \raisebox{-3pt}{\Envelope}  &(Removed)
    \end{tabular}
    }
}\\[10pt]


% <<<< NEW SECTION >>>>
\section{Projects and Awards}

    \raggedleft{\textsc{Current}}\par\raggedright
    Developing my own operating system from the ground up as a solo project. \\[5pt]

    \raggedleft{\textsc{August 2011}}\par\raggedright
    Outstanding intern finalist for The University of Illinois Research and Development park.
    Nominated by management for outstanding leadership.\\[5pt]


    \raggedleft{\textsc{Summer 2011}}\par\raggedright
    Member of a two person team that was tasked to increase the accuracy rates of a computer vision
    and recognition algorithm for State Farm. \\[5pt]

    \raggedleft{\textsc{Summer 2011}}\par\raggedright
    Project Lead for a seven member team researching augmented reality for State Farm.\\[10pt]



% <<<< NEW SECTION >>>>
\section{Memberships}
\textbf{Ubuntu Bugcontrol Member} \\[5pt]
Debugged issues related to the Mozilla Firefox web browser.
Gathered relevant information from users to aid in the debugging process.
\\[10pt]


\textbf{Association for Computing Machinery} \\[5pt]
Active member and volunteer.\\
Chair of SIGSoft - Special interest group for software engineering.
\\[15pt]




% <<<< NEW SECTION >>>>
\section{Computer Skills}

    \begin{tabular}{rl}
    Intermediate Knowledge: & C/C++ , Java, \textsc{Linux}, \\ 
                            & Windows\\
    \\
    Basic Knowledge:& OpenCV, PCL, Android, \\
                    & Subversion, Visual Studio, \\
                    & Eclipse, Git, {\LaTeX}, \\
                    & x86 and MIPS Assembly ISA \\
    \end{tabular}




\end{minipage} %END of right-hand side minipage

\end{document}
